Investigation of Limited Detection Schemes for Light Scattering of Optically Trapped Asymmetric Particles

### 2022-12-08 Manuscript_rev1.tex
Add files via upload

Since their invention in the late 1980's, Optical Tweezers have found application in experiments ranging from single molecule biophysics \cite{Bustamante2021Biophysics} to those that test the fundamental assumptions of Quantum Mechanics  \cite{yin2013large} thanks mainly to the ability of the tweezer to transduce and detect forces on the order of a few piconewtons. \textit{Further characterisation of the trapped entity would provide useful information, as explored in for example} metrological measurements \cite{arita2020coherent} and colloidal aggregation \cite{burns1990optical}. Chemical characterisation of the trapped entities has been achieved using spectroscopic techniques such as Raman Scattering \cite{gupta2014raman}, while dynamical characterisation has been demonstrated using a Quadrant Photo Detector,  by following the centre-of-mass Brownian motion of the trapped entity  \cite{friedrich2012tuning} and measuring rotation  of the centre-of-mass \cite{yifat2021facile}.

@@

To demonstrate the analysis, we study a simple, illustrative example
of a trapped entity more complex than a single sphere (i.e.\ a trapped
asymmetric dimer).  We explore how to optimise the experimental
measurement to obtain the best estimate of the dimer's instantaneous
orientation, as a further paradigmatic example of interpretation of
the scattering data to obtain dynamical information on the trapped
entity.  There is a paucity of literature on measuring the orientation
of trapped non-spherical particles till the recent attempt in
Ref.~\cite{raudsepp2022estimating} where imaging was employed to
study the orientation of trapped dimers and a resolution of () was
achieved.  Here, we simulate the Brownian motion of a dimer and
calculate the resulting scattered light, and show how Bayesian
inference can be used to optimise extraction of the true dimer
orientation from the light scattering signals given a choice of
scattering measurement angles.

@@

We use the Brownian OT package developed by Fung~\textit{et~al}. \cite{Vigilante2020Brownian_OT} to simulate the motion of a asymmetric dimer within an optical trap.  Brownian OT combines MSTM \cite{Mishchenko1996MSTM} and ``Optical Tweezer Toolbox'' (\textit{ott}) \cite{Lenton2020} to simulate the motion of arbitrary
shaped sphere clusters. We simulated the motion of a silica dimer
trapped in a $5$ mW Gaussian beam; the dimer was comprised of two tangent spheres with radii $1\,{\rm \mu m}$ and $ 0.5\,{\rm \mu m}$, respectively.  We ran our simulation over the span of 10 seconds, with Brownian OT calculating the dimer's orientation and position every $1 \ ms$.

@@

With any trapped particle there are two main sources of motion, Brownian and optical forces.  The dimer's Brownian motion ($\Delta q^{\textbf{B}}$) is simulated by generating a set of normally-distributed numbers whose covariance is given by the dimer's diffusion tensor $\textbf{D}$.  The diffusion tensor is computed based on Farsund's work \cite{Farsund1996}. For computing the optical force Brownian OT uses the T-Matrix method to calculate the scattering coefficients of the outgoing scattered wave.  The T-matrix describes the scattering process by relating the scattering wave to the incident wave:
\begin{align}
	\begin{pmatrix}
		p_{mn} \\
		q_{mn}
	\end{pmatrix}
	= \textbf{T}
	\begin{pmatrix}
		a_{mn} \\
		b_{mn}
	\end{pmatrix}
\end{align}
MSTM computes the T-matrix of the dimer, and then passes the T-matrix to \textit{ott} to compute the optical forces. The benefit of this approach is that MSTM can accurately compute the T-matrix for any arbitrary collection of spheres once, and then \textit{ott} can calculate the optical forces and torques. The total displacement is the sum of the optical and Brownian contributions:
\begin{align}
  \langle \Delta q_i^{\textbf{B}} \Delta q_j^{\textbf{B}}\rangle
  &= 2D_{ij} \Delta t
  \\
  \Delta q^{opt} &= \frac{\Delta t}{k_BT}\textbf{D} \cdot \textbf{F}
  \\
\Delta q^{tot} &= \Delta q^{\textbf{B}} + \Delta q^{opt}
\end{align}
where \textbf{F} is the a 6-component vector that describes the optical force and torque components.  Brownian OT returns the dimer's motion as a \textit{csv} file containing for each time step the $[x,y,z]$ position of the dimer's centre of mass relative to the trap focus, and the orientation represented as a quaternion.

@@

Our goal is to determine the orientation of our trapper dimer based on the scattering measurements $I(\hat{n}, \ \theta_k)$ collected from three detection fibres situated at $\theta_1,\ \theta_2, \ \& \ \theta_3$. Rather than get an exact estimate of the dimer's orientation the possible orientation space is discretised into $\textit{n}_{ref} \ = \ 30$ possible reference orientations $\hat{\bf n}_{\alpha}$ that are evenly distributed on a unit sphere \cite{Rey2006}. Using MSTM we compute the raw intensities that would be collected from the dimer in each reference orientation $I(\hat{\bf n}_{\alpha}, \theta_k)$. 
%
These raw intensities are normalised according to
\begin{align}
\label{eq:scale}
  y_k(\hat{\bf n}_\alpha)
  = 
  \frac{I(\hat{\bf n}_\alpha, \theta_k) - \langle I(\hat{\bf n},\theta_k) \rangle } 
  {\langle I^2(\hat{\bf n},\theta_k) \rangle -\langle I(\hat{\bf n}, \theta_k)\rangle^2}
\end{align}
where the denominator is simply the standard deviation for our values of $I(\hat{\bf n}, \theta_k)$. The reference orientations, raw intensities, and scaled signals are given in Tables~\ref{tab:A1} and \ref{tab:A2}.
%
In practice, $y_k(\bar{\bf s})$ will have an inherent amount of uncertainty in our measurement due to noise from our detector.  We can compare any instantaneous signal $y_1, y_2, y_3$ to our reference signals by assuming that the measurement uncertainty for each detection fibre is Gaussian and is centred about $y_k(\bar{\bf n})$.
%
Combining the signals from all three detection angles provides us with the conditional probability that, should the dimer be in orientation
$\hat{\bf n}_\alpha$, it would produce a signal ($y_1$, $y_2$, $y_3$):
\begin{align}
\label{eq:conditional}
  p(y_1, y_2, y_3|\hat{\bf n}_\alpha)
  = \prod^3_{k=1}
(2\pi\sigma_k^2)^{-1/2} 
e^{-(y_{k}-y_{k}(\hat{\bf n}_\alpha))^2/2\sigma_k^2}
\end{align}
where $\sigma_k$ is related to the uncertainty in the detected signal
from our dimer $y_k(\bar{\bf s})$.

We left this as a tuneable parameter to characterize the influence of experimental error on our predictive method.  The signal error was simulated in our model by stochastically adjusting our values of $y_k(\bar{\bf s})$.
\begin{eqnarray*}
  \sigma_k&=\epsilon\bar{y}(\hat{\bf n}_k)
  \\
  \Rightarrow y(\bar{\bf s}_k)&=y(\bar{\bf s})_k \pm n\sigma_k
  \\ 
n \in \mathbb{R},&n\in[0,1]
\end{eqnarray*} 
where $\epsilon$ is the percent error expected from our detection fibres.

Equation~\eqref{eq:conditional} gives the probability that a signal
($y_1$, $y_2$, $y_3$) will be measured if a dimer is in reference
orientation $\hat{\rm n}_\alpha$.
Using Bayes' theorem, the probability that the dimer is in reference orientation $\hat{\bf n}_\alpha$, given that the signal ($y_1$, $y_2$,
$y_3$) is measured, can be estimated:
%.
\begin{align}
  \label{eq:bayes}
  p(\hat{\bf n}_\alpha| y_1,y_2,y_3)
  &=
    \frac{p(y_1,y_2,y_3|\hat{\bf n}_\alpha)
    p(\hat{\bf n}_\alpha)}{p(y_1, y_2, y_3)}
\end{align}
where $p(\hat{\bf n}_\alpha)$ and $p(y_1, y_2, y_3)$ are the prior
estimates of the distributions of particle orientations and
instantaneous signals, respectively.
%
Without any prior evidence we assume that the orientation priori of our dimer
$p(\hat{\bf n}_{\alpha})$ is uniform. Knowledge of the dimer from previous
measurement can be used to inform our estimate of $p(\hat{\bf n}_{\alpha})$, covered in Section~\ref{sec:test}.  The latter prior $p(y)$ is the probability of measuring a signal ($y_1$, $y_2$, $y_3$).  This is given by taking the discrete integral over collection of reference orientations.
\begin{align}
  p(y_1, y_2, y_3)
  =
  \sum_{\alpha=1}^{n_{\rm ref}}
  p(y_1, y_2, y_3|\hat{\bf n}_\alpha)
  p(\hat{\bf n}_\alpha)
\end{align}
From \eqref{eq:bayes} we get a mass probability distribution that denotes the
probability that our dimer is in orientation $\hat{\bf n}_{\alpha}$ given a
signal ($y_1$, $y_2$, $y_3$). In order to evaluate the accuracy of our method, we tested it using a Brownian dynamics simulation of the dimer (see Section~\ref{sec:brownian}).

@@

To measure the error in the model's estimate the distribution from
Eq.~\eqref{eq:bayes} and an ideal result, $p_ideal$, were compared.  An ideal result would be one that is 0 for every $\hat{\bf n}$ apart from $\hat{\bf n}_{best}$.
\begin{align}
	p_{best} = 
	\begin{cases}
		1 & \text{when $\hat{\bf n}_\alpha$ = $\hat{\bf n}_{best}$}\\
		0 & \text{anywhere else}
	\end{cases}
\end{align}
The distribution from Eq.~\eqref{eq:bayes} will assign some non-zero
probability to every reference orientation. The model's error was measured by calculating the Kullback-Leibler divergence $K_l$ between the two distributions.
\begin{align}
	K_{l, \#}(p_{best}\parallel p(\hat{\bf n}_\alpha| y_1, y_2, y_3))
	= p_{best}\ln \left[\frac{p_{best}}{p(\hat{\bf n}| y_1,y_2,y_3))}
	\right]
	\label{eq;kullback}
\end{align}
where a larger value of $K_l$ indicates that our model is less confident in its 
prediction of the dimer's orientation. The divergence provides us a measure of how confident our measurement is. To better reflect the model's accuracy we implemented a penalty condition that worsens the divergence if our model estimates the wrong reference orientation:
\begin{align}
	p(\hat{\bf n}|y_1,y_2,y_3) = 
	\begin{cases}
		p(\hat{\bf n}_{estimate}|y_1,y_2,y_3) & 
		\text{when $\hat{\bf n}_{estimate}$ = $\hat{\bf n}_{best}$}\\
		p(\hat{\bf n}_{estimate}|y_1,y_2,y_3)-p(\hat{\bf n}_{best}|y_1,y_2,y_3) & \text{when $\hat{\bf n}_{estimate} \ne \hat{\bf n}_{best}$}
	\end{cases}
\end{align}

@@

Using our simulation from Section~\ref{sec:brownian} we calculated the instantaneous signal from our dimer at each time step using MSTM.  We applied Eq.~\eqref{eq:bayes} --- covered in Section~\ref{sec:Bayes} --- and the reference orientation with the highest probability is taken as our estimation of the dimer's instantaneous orientation. To visualise our model's performance  we plotted the radial distance between our estimation $\hat{\bf n}_{est}$ of the orientation and the dimer's \emph{actual} instantaneous orientation $\hat{\bf s}$ versus time. For comparison, we also plotted the radial distance between the closest reference orientation, denoted $\hat{\bf n}_{best}$, and the dimer's instantaneous orientation. The dotted line indicates the maximum radian distance ($0.896$ radians) between two neighbouring reference orientations, if we are under this line then we know our estimate and the best result are beside one another. If we assume our prior of the reference orientations $p(\hat{\bf n}_\alpha)$ to be uniform the performance is poor, as seen in Figure~\ref{fig:uniform}.

@@

\begin{align}
  p(\hat{\bf n}_\alpha)
  &=\frac{e^{\beta (\hat{\bf n}_\alpha (t) 
  	\cdot \hat{\bf n}_{est}(t-\Delta t))}}
  {\sum_{j=1}^{n_{\rm ref}}
	e^{\beta (\hat{\bf n}_\alpha (t) 
	\cdot \hat{\bf n}_{est}(t-\Delta t)}}
\end{align}

where $\beta$ is a weighting factor that controls the significance of our priori estimate. The simulation data from Section~\ref{sec:brownian} was used to evaluate our model's performance --- covered in Section~\ref{sec:divergence}. By summing the divergence of each measurement across the entire simulation we get an evaluation of how well the model performed in estimating the dimer's orientation. To compare the effects of changing certain parameters on the performance of our model we compare our result of $K_{l,total}$ to a worst case scenario and evaluate how much it improves upon this, denoted as $F(K_l)$:

@@

The Brownian OT software was used to simulate the motion of a trappeddimer ($a_1=1\,{\rm \mu m}$, $a_2=0.5\,{\rm \mu m}$) over the first
$10$ seconds of entering the optical trap.  The initial orientation was assumed as strictly vertical (in line with the beam propagation direction). The dimer's position orientation was recorded every $10\,{\rm \mu s}$ for using as a test dataset for our model.

@@

A key assumption of Eq.~\eqref{eq:conditional} is that we assume our detected light signal will inherently have some degree of noise. This is the central premise that allows us to form Eq.~\eqref{eq:conditional}, understanding the limits of acceptable signal error is necessary for implementing this to experimental work. To this end we ran our model while varying the value of $\epsilon$, Figure~\ref{fig:epsilon} shows the performance of the method with a selection of angles $15^{\circ}$, $55^{\circ}$, and $90^{\circ}$ and $\beta$ set to $1$:

@@

As can be seen from Figure~\ref{fig:epsilon}, there is a sweet spot for the signal error; with a $5$\% error giving an inaccurate estimation, and with a $25$\% error providing a satisfactory estimate but with sudden shifts away from the ideal result. A reason why our low error estimation performed so poorly is that the minimum difference between our values of $y_k$ is larger than our signal error. As such the model could not distinguish between different reference orientations and was essentially just picking options at random. This minimum difference determined by our choice of angles and sets a lower limit of how accurate our signals can be. In the future we hope to look at increasing the number of reference orientations to see what the true lower bound is.

>>>>

Since their invention in the late 1980's, Optical Tweezers have found application in experiments ranging from single molecule biophysics \cite{Bustamante2021Biophysics} to those that test the fundamental assumptions of Quantum Mechanics  \cite{yin2013large} thanks mainly to the ability of the tweezer to transduce and detect forces on the order of a few pico newtons. \textit{Further characterisation of the trapped entity would provide useful information, as explored in for example} metrological measurements \cite{arita2020coherent} and colloidal aggregation \cite{burns1990optical}. Chemical characterisation of the trapped entities has been achieved using spectroscopic techniques such as Raman Scattering \cite{gupta2014raman}, while dynamical characterisation has been demonstrated using a Quadrant Photo Detector,  by following the centre-of-mass Brownian motion of the trapped entity  \cite{friedrich2012tuning} and measuring rotation  of the centre-of-mass \cite{yifat2021facile}.

@@

To demonstrate the analysis, we study a simple, illustrative example of a trapped entity more complex than a single sphere (i.e.\ a trapped asymmetric dimer).  We explore how to optimise the experimental measurement to obtain the best estimate of the dimer's instantaneous orientation, as a further paradigmatic example of interpretation of the scattering data to obtain dynamical information on the trapped entity. There is a paucity of literature on measuring the orientation of trapped non-spherical particles till the recent attempt in Ref.~\cite{raudsepp2022estimating} where imaging was employed to study the orientation of trapped dimers.  Here, we simulate the Brownian motion of a dimer and calculate the resulting scattered light, and show how Bayesian inference can be used to optimise extraction of the true dimer orientation from the light scattering signals given a choice of scattering measurement angles.

@@

We use the Brownian OT package developed by Fung~\textit{et~al}. \cite{Vigilante2020Brownian_OT} to simulate the motion of a asymmetric dimer within an optical trap. Brownian OT combines MSTM \cite{Mishchenko1996MSTM} and ``Optical Tweezer Toolbox'' (\textit{ott}) \cite{Lenton2020} to simulate the motion of arbitrary
shaped sphere clusters. We simulated the motion of a silica dimer
trapped in a highly focused Gaussian beam.

@@

The dimer's Brownian motion is simulated by calculating its diffusion tensor according to Farsund's \emph{et al} work \cite{Farsund1996}. For computing the optical force Brownian OT uses the T-Matrix method to calculate scattering of the dimer. MSTM computes the T-matrix of the dimer, and then passes the T-matrix to \textit{ott} to compute the optical forces. The benefit of this approach is that MSTM can accurately compute the T-matrix for any arbitrary collection of spheres once, and then \textit{ott} can calculate the optical forces and torques. The total displacement is the sum of the optical and Brownian contributions.

Brownian OT returns the dimer's motion as a \textit{csv} file containing for each time step the $[x,y,z]$ position of the dimer's centre of mass relative to the trap focus, and the orientation represented as a quaternion.

@@

Our goal is to determine the orientation of our trapper dimer based on the scattering measurements $I(\hat{n}, \ \theta_k)$ collected from three detection fibres situated at $\theta_1,\ \theta_2, \ \& \ \theta_3$. Rather than get an exact estimate of the dimer's orientation the possible orientation space is discretized into $\textit{n}_{ref} \ = \ 30$ possible reference orientations $\hat{\bf n}_{\alpha}$ that are evenly distributed on a unit sphere \cite{Rey2006}. Using MSTM we compute the raw intensities that would be collected from the dimer in each reference orientation $I(\hat{\bf n}_{\alpha}, \theta_k)$. 
%
These raw intensities are normalized according to
\begin{align}
\label{eq:scale}
  y_k(\hat{\bf n}_\alpha)
  = 
  \frac{I(\hat{\bf n}_\alpha, \theta_k) - \langle I(\hat{\bf n},\theta_k) \rangle } 
  {\langle I^2(\hat{\bf n},\theta_k) \rangle -\langle I(\hat{\bf n}, \theta_k)\rangle^2}
\end{align}
where the denominator is simply the standard deviation for our values of $I(\hat{\bf n}, \theta_k)$. The reference orientations, raw intensities, and scaled signals are given in Tables~\ref{tab:A1} and \ref{tab:A2}. The distribution of collected signals bares no specific relationship with its associated reference orientation, in some cases different reference orientations will have identical signals. This is an inherent challenge of the inverse light scattering problem, fortunately we can apply statistical techniques to resolve the lack of relationship between orientation and scattering.

In practice, $y_k(\hat{\bf s})$ will have an inherent amount of uncertainty in its measurement. We can compare any instantaneous signal $y_1, y_2, y_3$ to our reference signals by assuming that the measurement uncertainty is Gaussian and is centred about $y_k(\hat{\bf n}_\alpha)$.
%
Combining the signals from all three detection angles provides us with the conditional probability that, should the dimer be in orientation
$\hat{\bf n}_\alpha$, it would produce a signal ($y_1$, $y_2$, $y_3$):
\begin{align}
\label{eq:conditional}
  p(y_1, y_2, y_3|\hat{\bf n}_\alpha)
  = \prod^3_{k=1}
(2\pi\sigma_k^2)^{-1/2} 
e^{-(y_{k}-y_{k}(\hat{\bf n}_\alpha))^2/2\sigma_k^2}
\end{align}
where $\sigma_k$ is related to the uncertainty in our measurement $y_k(\hat{\bf s})$. We left this as a tuneable parameter to determine the influence of experimental error on our predictive method. To simulate uncertainty in our measurement we stochastically adjusted our values of $y_k(\hat{\bf s})$. Equation~\eqref{eq:conditional} gives the probability that a signal ($y_1$, $y_2$, $y_3$) will be measured if a dimer is in reference orientation $\hat{\rm n}_\alpha$. Using Bayes' theorem, the probability that the dimer is in reference orientation $\hat{\bf n}_\alpha$, given that the signal ($y_1$, $y_2$, $y_3$) is measured, can be estimated:
%.
\begin{align}
  \label{eq:bayes}
  p(\hat{\bf n}_\alpha| y_1,y_2,y_3)
  &=
    \frac{p(y_1,y_2,y_3|\hat{\bf n}_\alpha)
    p(\hat{\bf n}_\alpha)}{p(y_1, y_2, y_3)}
\end{align}
where $p(\hat{\bf n}_\alpha)$ and $p(y_1, y_2, y_3)$ are the prior estimates of the distributions of particle orientations and instantaneous signals, respectively.
%
Without any prior evidence we assume that the orientation priori of our dimer
$p(\hat{\bf n}_{\alpha})$ is uniform. Knowledge of the dimer from previous
measurement can be used to inform our estimate of $p(\hat{\bf n}_{\alpha})$, covered in Section~\ref{sec:test}.  The latter prior $p(y)$ is the probability of measuring a signal ($y_1$, $y_2$, $y_3$).  This is given by taking the discrete integral over collection of reference orientations.
\begin{align}
  p(y_1, y_2, y_3)
  =
  \sum_{\alpha=1}^{n_{\rm ref}}
  p(y_1, y_2, y_3|\hat{\bf n}_\alpha)
  p(\hat{\bf n}_\alpha)
\end{align}
From \eqref{eq:bayes} we get a mass probability distribution that denotes the
probability that our dimer is in orientation $\hat{\bf n}_{\alpha}$ given a
signal ($y_1$, $y_2$, $y_3$). In order to evaluate the accuracy of our method, we tested it using a Brownian dynamics simulation of the dimer (see Section~\ref{sec:brownian}).

@@

To measure the error in the model's estimate the distribution from
Eq.~\eqref{eq:bayes} and an ideal result, $p_ideal$, were compared.  An ideal result would be one that is 0 for every $\hat{\bf n}$ apart from $\hat{\bf n}_{best}$.
\begin{align}
	p_{best} = 
	\begin{cases}
		1 & \text{when $\hat{\bf n}_\alpha$ = $\hat{\bf n}_{best}$}\\
		0 & \text{anywhere else}
	\end{cases}
\end{align}
The distribution from Eq.~\eqref{eq:bayes} will assign some non-zero
probability to every reference orientation. The model's error was measured by calculating the Kullback-Leibler divergence $K_l$ between the two distributions.
\begin{align}
	K_{l, \#}(p_{best}\parallel p(\hat{\bf n}_\alpha| y_1, y_2, y_3))
	= p_{best}\ln \left[\frac{p_{best}}{p(\hat{\bf n}| y_1,y_2,y_3))}
	\right]
	\label{eq;kullback}
\end{align}
where a larger value of $K_l$ indicates that our model is less confident in its 
prediction of the dimer's orientation. The divergence provides us a measure of how confident our measurement is. To better reflect the model's accuracy we implemented a penalty condition that worsens the divergence if our model estimates the wrong reference orientation:
\begin{align}
	p(\hat{\bf n}|y_1,y_2,y_3) = 
	\begin{cases}
		p(\hat{\bf n}_{est}|y_1,y_2,y_3) & 
		\text{when $\hat{\bf n}_{estimate}$ = $\hat{\bf n}_{best}$}\\
		p(\hat{\bf n}_{est}|y_1,y_2,y_3)-p(\hat{\bf n}_{best}|y_1,y_2,y_3) & \text{when $\hat{\bf n}_{est} \ne \hat{\bf n}_{best}$}
	\end{cases}
\end{align}

@@

Using our simulation from Section~\ref{sec:brownian} we simulated the motion of a silica dimer trapped within a 5 mW optical trap. The dimer is comprised of two tangent spheres with radii $1 \mu m$ and $0.5 \mu m$ respectively. We simulated the first 10 seconds of motion, calculating the orientation and position every 1 ms.

We applied Eq.~\eqref{eq:bayes} --- covered in Section~\ref{sec:Bayes} --- and the reference orientation with the highest probability is taken as our estimation of the dimer's instantaneous orientation. To visualise our model's performance  we plotted the radial distance between our estimation $\hat{\bf n}_{est}$ of the orientation and the dimer's \emph{actual} instantaneous orientation $\hat{\bf s}$ versus time. For comparison, we also plotted the radial distance between the closest reference orientation, denoted $\hat{\bf n}_{best}$, and the dimer's instantaneous orientation. The dotted line indicates the maximum radian distance ($0.896$ radians) between two neighbouring reference orientations, if we are under this line then we know our estimate and the best result are beside one another. If we assume our prior of the reference orientations $p(\hat{\bf n}_\alpha)$ to be uniform the performance is poor, as seen in Figure~\ref{fig:uniform}.

@@

\begin{align}
  p(\hat{\bf n}_\alpha)
  &=\frac{e^{\beta (\hat{\bf n}_\alpha (t) 
  	\cdot \hat{\bf n}_{est}(t-\Delta t))}}
  {\sum_{\alpha=1}^{n_{\rm ref}}
	e^{\beta (\hat{\bf n}_\alpha (t) 
	\cdot \hat{\bf n}_{est}(t-\Delta t)}}
\end{align}

where $\beta$ is a weighting factor that describes the dimer's freedom of motion within the trap. By summing over each reference orientation $p(\hat{\bf n}_\alpha)$ is normalized. The simulation data from Section~\ref{sec:brownian} was used to evaluate our model's performance --- covered in Section~\ref{sec:divergence}. By summing the divergence of each measurement across the entire simulation we get an evaluation of how well the model performed in estimating the dimer's orientation. To compare the effects of changing certain parameters on the performance of our model we compare our result of $K_{l,total}$ to a worst case scenario and evaluate how much it improves upon this, denoted as $F(K_l)$:

@@

The Brownian OT software was used to simulate the motion of a trapped dimer ($a_1=1\,{\rm \mu m}$, $a_2=0.5\,{\rm \mu m}$) over the first $10$ seconds of entering the optical trap.  The initial orientation was assumed as strictly vertical (in line with the beam propagation direction). The dimer's position orientation was recorded every 1 ms for using as a test dataset for our model.

@@

A key assumption of Eq.~\eqref{eq:conditional} is that we assume our measurement of scattering signals will inherently have some degree of uncertainty. This is the central premise that allows us to form Eq.~\eqref{eq:conditional}. In an experimental situation the most common source of uncertainty is from the detection bias. Therefore, understanding the limits of acceptable uncertainty is necessary for implementing this to experimental work. To this end we redefine $\sigma_k$ as the average reference signal $\bar{y}(\hat{\bf n}_\alpha)$ multiplied by the percent error caused by the signal detectors:
\begin{align}
	\sigma_k = \epsilon \bar{y}(\hat{\bf n}_\alpha)
\end{align} 
We ran our model while varying the value of $\epsilon$, Figure~\ref{fig:epsilon} shows the performance of the method with a selection of angles $15^{\circ}$, $55^{\circ}$, and $90^{\circ}$ and $\beta$ set to $1$:

@@

As can be seen from Figure~\ref{fig:epsilon}, there is a sweet spot for the signal error; with a $5$\% error giving an inaccurate estimation, and with a $25$\% error providing a satisfactory estimate but with sudden shifts away fromthe ideal result. A reason why our low error estimation performed so poorly is that the minimum difference between our values of $y_k$ is larger than our signal error. As such the model could not distinguish between different reference orientations and was essentially just picking options at random. This minimum difference determined by our choice of angles and sets a lower limit of how accurate our signals can be. In the future we hope to look at increasing the number of reference orientations to see what the true lower bound is.
